---
title: "Week4 Assignment"
author: "Emre Kemerci"
date: "November 20, 2018"
output: html_document
---

```{r}
library(tidyverse)
```


```{r, warning=FALSE}
data<-readRDS(file = "C:/Users/emrek/Google Drive/BDA/503-EssentialsOfDataAnalytics/GitHub/pj18-EmreKemerci/AssignmentWeek4/car_data_aggregate.rds")

```

first, take a glance at variables

```{r}
data %>% str()

UniqueBrandNames<-data %>% distinct(brand_name)
UniqueYear<-data %>% distinct(year)
UniqueMonth<-data %>% distinct(month)
list(c(UniqueBrandNames,UniqueMonth, UniqueYear))
```

Month and Year variables have appropriate values but brand_names variable needs cleaning since there are "TOPLAM:" and "ODD, verilerinde..." values. Also, brand_name has values "Aston MARTÝN and Aston MARTIN", we can replace "Aston MARTÝN"" with "Aston MARTIN". 

```{r, warning=FALSE}

data <- data %>% filter(!grepl("ODD", brand_name) & brand_name!="TOPLAM:")

data <- data %>%
  mutate(brand_name=replace(brand_name,brand_name=="ASTON MARTÝN","ASTON MARTIN"))


```

I want to analyse market shares of each brand for auto sales, commercial vehicle sales and total sales.

```{r}
market_shares <- data %>%
  group_by(brand_name) %>%
  summarize(auto_grand_total=sum(auto_total), comm_grand_total=sum(comm_total), total_grand_total=sum(total_total)) %>%
  mutate(auto_market_share=round((auto_grand_total/sum(auto_grand_total)),4)) %>% 
  mutate (comm_market_share=round((comm_grand_total/sum(comm_grand_total)),4)) %>%
  mutate (total_market_share=round((total_grand_total/sum(total_grand_total)),4))
  
```

lets visualize


```{r}
library(ggplot2)
ggplot(market_shares, 
       aes(x=total_market_share,
           y=comm_market_share, color=brand_name
           )) +
      geom_point() +
      
      expand_limits(x=0)
      
    


```

