---
title: "Week4 Assignment"
author: "Emre Kemerci"
date: "November 20, 2018"
output: html_document
---

```{r, warning=FALSE}
library(tidyverse)
```

To read the aggregated ODD sales data for the monthly periods between Jan 2016 - Sep 2018.

```{r, warning=FALSE}
data<-readRDS(file = "C:/Users/emrek/Google Drive/BDA/503-EssentialsOfDataAnalytics/GitHub/pj18-EmreKemerci/AssignmentWeek4/car_data_aggregate.rds")

```

first, take a glance at variables

```{r}
data %>% glimpse()

data %>% distinct(brand_name)
data %>% distinct(year)
data %>% distinct(month)


```

Month and Year variables have appropriate values but brand_names variable needs cleaning since there are "TOPLAM:" and "ODD, verilerinde..." values. Also, brand_name has values "Aston MARTÝN and Aston MARTIN", we can replace "Aston MARTÝN"" with "Aston MARTIN". 

```{r, warning=FALSE}

data <- data %>% filter(!grepl("ODD", brand_name) & brand_name!="TOPLAM:")

data <- data %>%
  mutate(brand_name=replace(brand_name,brand_name=="ASTON MARTÝN","ASTON MARTIN"))


```

I want to analyse market shares over sales between 2016-2018/9 of each brand for auto sales, commercial vehicle sales and total sales.

```{r}
market_shares <- data %>%
  group_by(brand_name) %>%
  summarize(auto_grand_total=sum(auto_total), comm_grand_total=sum(comm_total), total_grand_total=sum(total_total)) %>%
  mutate(auto_market_share=round((auto_grand_total/sum(auto_grand_total)),4)) %>% 
  mutate (comm_market_share=round((comm_grand_total/sum(comm_grand_total)),4)) %>%
  mutate (total_market_share=round((total_grand_total/sum(total_grand_total)),4))
market_shares
  
```

```{r, warning=FALSE}
market_shares_summary <- market_shares %>% select(brand_name, auto_market_share, comm_market_share)


library(reshape2)
  melt_summary <- melt(market_shares_summary, id=c("brand_name"))

melt_summary


```


lets visualize

```{r}
library(ggplot2)

ggplot(melt_summary, aes(x=brand_name, y=value*100, fill=variable)) +
    geom_bar(stat='identity', position= "dodge") +
     theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
      theme(legend.position = c(0.7, 0.75)) + 
        scale_y_continuous(sec.axis = sec_axis(~.,"Market Share (%)")) +
        labs(x="Brand Name", y="Market Share (%)", title="Market share of each brand according to sales between Jan 2016 - Sep 2018", fill=guide_legend(title="Vehicle Type")) + 
  scale_color_manual(name="Mileage", labels = c("Above Average", "Below Average")) +
          theme(legend.background = element_rect(fill="lightblue", size=0.5, linetype="solid"))
  

        
  
```



```{r}
gr<-market_shares %>%
  select(brand_name, total_market_share)

gr$share_z <- round((gr$total_market_share - mean(gr$total_market_share))/sd(gr$total_market_share), 2)

gr$marketshare_type <- ifelse(gr$share_z < 0, "below", "above")  
gr <- gr[order(gr$share_z), ]
gr$brand_name <- factor(gr$brand_name, levels = gr$brand_name)


theme_set(theme_bw())

ggplot(gr, aes(x=brand_name, y=share_z, label=share_z)) + 
  geom_point(stat='identity', aes(col=marketshare_type), size=6)  +
  scale_color_manual(name="Market Share", 
                     labels = c("Above Average", "Below Average"), 
                     values = c("above"="#00ba38", "below"="#f8766d")) + 
  geom_text(color="white", size=2) +
  labs(title="Diverging Dot Plot", 
       subtitle="Normalized total market shares") + 
  ylim(-2.5, 2.5) +
  coord_flip()


```

